Numerical simulation of the shallow water circular hydraulic jump

### 2020-06-11 numerics_paper/numerical_chj.tex
Add introductory material.

>>>>

In \cite{peery1988blunt} a particular instability was observed to
appear in numerical simulation of a bow shock, near the symmetry plane.
This phenomenon, known as a ``carbuncle", has been observed by many researchers
in similar numerical experiments for the Euler equations, and many remedies
have been proposed, mainly in the form of additional numerical dissipation
\cite{quirk1997contribution,pandolfi2001numerical,dumbser2004matrix,chauvat2005shock,ismail2009proposed,shen2014stability}.
Most notably, the HLLE Riemann solver suppresses the carbuncle instability \cite{quirk1997contribution}.
For a recent review of numerical shock instability and work to alleviate it,
we refer to \cite[Section 2.5]{simonnumerical}.

Given the similarity of structure between the Euler equations and the shallow
water equations, one might expect carbuncles to appear in numerical
solutions of the latter as well.  Indeed, this has been observed \cite{kemm2014note}.
The shallow water carbuncle behaves in a fashion very similar to the
Euler carbuncle: it appears when the Roe solver is used, but not when
the HLL solver is used, and at least some of the other methods that suppress
the latter also suppress the former \cite{kemm2014note,bader2014carbuncle}.

Meanwhile, some research has suggested that the carbuncle is not purely a
numerical instability but instead is the manifestation of a true physical
instability \cite{moschetta2001carbuncle,elling2009carbuncle}.
